---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# semanticscholar

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

The goal of `semanticscholar` is to offer data access to data from Semantic Scholar through their lightweight API which can provide data on publications and authors. Semantic Scholar is a free, non-profit academic search and discovery engine whose mission is to empower researchers.

## Installation

You can install the current version of `semanticscholar` from [GitHub](https://github.com/kth-library/semanticscholar) with:

``` r
#install.packages("devtools")
devtools::install_github("kth-library/semanticscholar", dependencies = TRUE)
```

## Example

This is a basic example which shows you how to get information for papers and authors:

```{r example}

library(semanticscholar)
library(dplyr)
suppressPackageStartupMessages(library(purrr))
library(knitr)

# get a paper using an identifier
paper <- S2_paper("arXiv:1705.10311", include_unknown_refs = TRUE)

# authors on that paper
authors <- paper$authors

# for one of the authors
author_ids <- authors$authorId
author <- S2_author(author_ids[1])

# list some of the papers
papers <- 
  author$papers %>% 
  select(title, year)

papers %>% head(5) %>% knitr::kable()

# get data from several identifiers for importing into Zotero
ids <- c("10.1038/nrn3241", "CorpusID:37220927")
my_refs <- zotero_references(ids)

# this data can now be imported via the Zetero API using https://github.com/giocomai/zoteroR
# showing data form the first record
my_refs[[1]]$journalArticle %>% glimpse()
my_refs[[2]]$creators %>% knitr::kable()

```

## Data source attribution

When data from `semanticscholar` is displayed publicly, this attribution also needs to be displayed:

`r S2_attribution()`
